cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_cubic

>>>>

The `gen_cubic(n, p, range)` function generates a dataset of $n$ points forming a cubic curve in the first two dimensions of a $p$-dimensional space. This function creates a more complex curvilinear structure than a simple parabola.

The shape is generated using a third-degree raw polynomial basis expansion. Let $X\_1 \sim \mathcal{U}(\text{range}\[1], \text{range}\[2])$ be the base input. A cubic transformation with vertical jitter is used to define $X\_2 = X\_1 + X\_1^2 - X\_1^3 + \varepsilon\_2\$, where \$\varepsilon\_2 \sim \mathcal{U}(0, 0.5)$.

When $p > 2$, the remaining dimensions consist of independent Gaussian noise features generated via `gen_noisedims()`:

$$
X\_j \sim \mathcal{N}(0, 0.1^2)\$ for \$j = 3, \dots, p.
$$
